Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-05 paper/ms.tex
update manuscript
the corner plot aspect ratio is now better

Finding and understanding systems undergoing these evolutionary
changes is a major goal in contemporary exoplanet research.  To
identify stars younger than say 1 \replaced{Gyr}{gigayear}, a number
of direct and indirect methods are available
\citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between \replaced{$0.68\,R_{\rm Jup}$
    and $0.97\,R_{\rm Jup}$}{$0.62\,R_{\rm Jup}$ and $0.95\,R_{\rm
    Jup}$} (3$^{\rm rd}$--97$^{\rm th}$ percentile).  This plot was
    made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

>>>>

Finding and understanding systems undergoing these evolutionary
changes is a major goal in contemporary exoplanet research.  To
identify stars younger than say 1 \replaced{Gyr}{gigayear}, a number
of direct and indirect methods are available
\citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{sanchis-ojeda_kepler-63b_2013}, \citet{david_discovery_2018},
and G{.}~Zhou et al{.}~(2020, submitted) have combined these methods
to age-date individual field stars hosting transiting planets.  Many
of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between \replaced{$0.68\,R_{\rm Jup}$
    and $0.97\,R_{\rm Jup}$}{$0.62\,R_{\rm Jup}$ and $0.95\,R_{\rm
    Jup}$} (3$^{\rm rd}$--97$^{\rm th}$ percentile).  This plot was
    made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}
